### 2018-08-13 introduction.tex
grammar mostly

Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 
5, 6, 8, 9) use a set of all nuclides in depletion calculations.

Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where 
material is moved to or from the core at all times (continuous) or at specific 
time steps (batch). To account for batch discharge, a depletion tool must 
remove some or all material at specified intervals. This requires the burn-up 
simulation to stop at a given time and restart with a new liquid fuel 
composition (after removal of discarded materials and addition of 
fissile/fertile materials). Accounting for a continuous removal or addition is 
more difficult because it requires adding a term to the Bateman equations. In 
SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set 
of Bateman equations using spectrum-averaged fluxes and cross sections 
generated from a deterministic transport calculation. Methods (1, 4, 8) model 
true continuous feeds and removals, while other methods employ a batch-wise 
approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based 
script for SCALE/TRITON which uses a semi-continuous batch process to simulate 
a continuous reprocessing. This tool models salt treatment, separations, 
discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small 
time steps to simulate continuous reprocessing and deplete the fuel salt 
\cite{powers_new_2013}.

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
simplified unit-cell geometry because depletion computations for a many-year 
fuel cycle are computationally expesive even for simple models.

Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: 
one for salt channels, one for two salt plena above and below the core and the 
last cell for the annulus, consequently, two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and 
clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
one-region models may produce reliable results for homogeneous reactor cores 
(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
(i.e. \gls{MSRE}). A two-region \gls{MSBR} must be simulated using a whole-core 
model to represent different neutron transport in the inner and outer regions 
of the core, because most fissions happens in the inner region while breeding 
occurs in the outer zone.

Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
employed it to study the material isotopic evolution of the \gls{MSFR}. The 
developed extension directly takes into account the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure 
\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
isotopic evolution. We employed this extended SERPENT 2 for a simplified 
unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
results which contradict existing \gls{MSBR} depletion simulations 
\cite{jeong_equilibrium_2016}.

The present work introduces the online reprocessing simulation code, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which 
represents the continuation of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
the equilibrium core composition and core depletion. The additional objective 
is to compare predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
determined and \gls{MSBR} fuel cycle performance will be analyzed.

The \gls{MSBR} complex geometry is hard to describe in software input, and, 
usually, researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. Note that this study leverages extensive computational 
resources to avoid these geometric approximations and accurately capture 
breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
related to circulating liquid fuel, is not treated here.

>>>>

Methods (1, 3, 4) simulate some form of reactivity control, and methods (1, 4, 
5, 6, 8, 9) use a set of all nuclides in depletion calculations.

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which 
material moves to and from the core at all times (continuous) or at specific 
time steps (batch). To account for batch discharge, a depletion tool must 
remove some or all material at specified intervals. This requires the burn-up 
simulation to stop at a given time and restart with a new liquid fuel 
composition (after removal of discarded materials and addition of 
fissile/fertile materials). Accounting for continuous removal or addition  
presents a greater challenge since it requires adding a term to the Bateman 
equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} 
solves a set of Bateman equations using spectrum-averaged fluxes and cross 
sections generated from a deterministic transport calculation. Methods (1, 4, 
8) model true continuous feeds and removals, while other methods employ a 
batch-wise approach. \gls{ORNL} researchers have developed ChemTriton, a 
Python-based script for SCALE/TRITON which uses a semi-continuous batch process 
to simulate a continuous reprocessing. ChemTriton models salt treatment, 
separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON 
model over small time steps to simulate continuous reprocessing and deplete the 
fuel salt \cite{powers_new_2013}.

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
simplified unit-cell geometry because depletion computations for a many-year 
fuel cycle are computationally expensive even for simple models.

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
one-region models may produce reliable results for homogeneous reactor cores 
(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
(i.e. \gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
employed it to study the material isotopic evolution of the \gls{MSFR}. The 
developed extension directly accounts for the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure 
\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
isotopic evolution. We employed this extended SERPENT 2 for a simplified 
unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
results which contradict existing \gls{MSBR} depletion simulations 
\cite{jeong_equilibrium_2016}.

The present work introduces the online reprocessing simulation code, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyze \gls{MSBR} neutronics and fuel cycle to find 
the equilibrium core composition. The additional objective 
is to compare predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
determined and \gls{MSBR} fuel cycle performance will be analyzed.

The complex \gls{MSBR} geometry is challenging to describe in software input, and, 
usually, researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. This study leverages extensive computational 
resources to avoid these geometric approximations in order to accurately capture 
breeding behavior.
